---
title: "What the Package Does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the Package Does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753Myka24)
```

# Introduction

The MATH4753Myka24 package provides a collection of functions for various statistical computations and simulations. This vignette serves as a guide to understanding and utilizing these functions effectively.


## Plot a normal distribution: `myncurve`

The `myncurve` function plots a normal distribution and calculates cumulative probability up to a specified value. Example:

```{r}
# Plot a normal distribution with mean=4, sigma=2, and calculate cumulative probability up to 3
myncurve(4, 2, 3)
```

Explanation: This code plots a normal distribution with a mean of 4 and a standard deviation of 2. It shades the area under the curve up to the value of 3 and calculates the cumulative probability up to that point.

## Monte Carlo simulation: `mycltu`

The `mycltu` function generates a Monte Carlo simulation for estimating the distribution of sample means drawn from a uniform distribution. Example:

```{r}
# Generate a Monte Carlo simulation with sample size = 100 and 1000 iterations
mycltu(100, 1000)
```

Explanation: This code generates a Monte Carlo simulation with a sample size of 100 and 1000 iterations. It plots a histogram and density plot of the sample means along with theoretical density curves.


## Maximum Likelihood Estimation: `mymaxlik`

The `mymaxlik` function estimates the maximum likelihood of parameters for repeated sampling from the same distribution. Example:

```{r}
# Example with binomial distribution
y <- c(3, 3, 4, 3, 4, 5, 5, 4)
logbin <- function(x, param) log(dbinom(x, prob = param, size = 20))
mymaxlik(logbin, y, seq(0, 1, length = 1000), main = "Binomial n = 20")
```

Explanation: This code demonstrates the usage of `mymaxlik` function with a binomial distribution likelihood function.


## Bootstrap Confidence Interval Estimation: `myboot`

The `myboot` function calculates bootstrap confidence intervals for a given statistic based on resampling with replacement. Example:

```{r}
# Generate bootstrap confidence interval for mean with 10000 iterations
set.seed(42)
data <- rnorm(100, mean = 10, sd = 2)
boot_result <- myboot(iter = 10000, x = data, fun = "mean", alpha = 0.05)
boot_result$ci
```

Explanation: This code computes a bootstrap confidence interval for the mean of a dataset with 10000 iterations and a significance level of 0.05.


## Dataset: fire

The `fire` dataset contains information about home damage from fire, including the distance from the fire station and the amount of damage in thousands of dollars.

```{r}
# Load the fire dataset
data(fire)

# Display the structure of the dataset
str(fire)

# Display the first few rows of the dataset
head(fire)
```

Explanation:

    The fire dataset consists of 15 rows and 2 variables: DISTANCE (distance from the fire station in miles) and DAMAGE (amount of damage in thousands of dollars).
    You can access more information about the dataset and its source in the documentation provided.
